The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-11 draft/ms.tex
Revision of Sec 3 and other misc revisions.

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer to keep track of the exoplanet
discoveries and catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted by exoplanets.org, which also hosts the Exoplanets
Data Explorer, an interactive table with plotting tools including all
the EOD exoplanets as well as other confirmed exoplanets (and now also
KOIs). The entire dataset of exoplanets.org is available for download
as a single {\tt .csv} file at the website's front page.\footnote{At
  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet researches (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visitors in 2013
according to Google Analytics.

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope and we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters of the exoplanet systems and host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. We also describe the updates to the
hosting website, exoplanets.org. The Exoplanet Data Explorer at
exoplanets.org has expanded its scope and now includes the
\kepler\ exoplanet candidates (KOIs). We describe these changes in
Section~\ref{sec:kepler}. The website has also gone through major
back-end changes since \cite{Wright2011}, which is described in
Section~\ref{sec:website}.

@@

KDE: obselete field! Detele from the table.

@@

Since \cite{Wright2011}, as more planets were discovered by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database. We are going to explain what they are and the criteria we used to put them into the EOD.

{\bf KOI}'s: Although KOI's are not counted as part of the EOD due to their status of being `candidates', we include them in our website so that these KOIs are put into the context of all confirmed exoplanets. To display the KOIs in the EDE table, check the 'Kepler' option on the upper left of the table (default selection only includes 'Orbit Database' and 'Other'). The KOIs listed in our table include two past Kepler data releases and the most up-to-date release from February 2014. The original data are from the NASA Exoplanet Archive.

ZZZ Ask Jason about their criteria. \\
We also included robustly detected imaging, microlensing, and timing planets and the criteria are the following (as set by the QUACBED):

@@

\end{itemize}
Planets primarily detected by these methods do not have robust orbital parameters and they are categorized as ``Other Planets'' on
exoplanets.org. If planets have follow up radial velocity or transit observations and thus have good orbital parameters, they have the EOD flags. See Section~\ref{sec:kepler} for more information about `Other Planets'. These other planets can be displayed by check the `Other' option for the table. They are not included in the EOD (especially some microlensing and imaging planets) because of poorly characterized orbits.

Also add our criteria for vetting IMAGING planets, which can be found
here: http://exoplanets.org/methodology.html; do we have any similar
criteria for Microlensing, timing and astrometry planets? Like mass
cut etc.?

Figure: some comparison figures of Kepler candidate properties
vs. EOD planet properties, such as mass-period, mass-radius?

@@

KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata & \ref{sec:disc} \\

>>>>

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
discoveries and catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted by exoplanets.org, which also hosts the EDE, an
interactive table with plotting tools including all the EOD exoplanets
as well as other confirmed exoplanets (and now also KOIs). The entire
dataset of exoplanets.org is available for download as a single {\tt
  .csv} file at the website's front page.\footnote{At
  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet researches (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visitors in 2013
according to Google Analytics.

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope and we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters of the exoplanet systems and host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. We also describe the updates to the
hosting website, exoplanets.org. The EDE at exoplanets.org has
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website has also gone through major back-end changes since
\cite{Wright2011}, which is described in Section~\ref{sec:website}.

@@

%KDE: obselete field! Detele from the table.

@@

Since \cite{Wright2011}, as more planets were robustly discovered by
different methods other than radial velocity and transit, we have
expanded our database at exoplanets.org to better ingest those
planets.

% KOIs
First, we now include the KOIs discovered by \kepler in the
EDE. Although KOIs are not counted as part of the EOD due to their
status of being `candidates', we include them in our website so that
these KOIs are put into the context of all confirmed exoplanets. The
KOIs listed in our table include three Kepler data releases (as of
March 2014), and we always keep up with the most up-to-date
releases. The original data are from the NASA Exoplanet Archive.

To display the KOIs in the EDE table, check the 'Kepler' option on the
upper left of the table (default selection only includes 'Orbit
Database', i.e.~the EOD, and 'Other'). They can also be displayed on
plots with the interactive plotting tool of EDE.

% Other Planets
ZZZ Ask Jason about their criteria. \\ Second, we now also include
robustly detected imaging, microlensing, and timing planets, and our
criteria for a `robust detection' are the following (as set by the
QUACBED):

@@

\end{itemize}
Some of the exoplanets primarily detected by these methods do not have
well-determined orbital parameters, and thus they are categorized as
``Other Planets'' on exoplanets.org instead of being in the EOD. These
planets can be displayed by check the `Other' option for the EDE
table. As of March 2014, no microlensing or imaging planets are in the
EOD, while several timing exoplanets have well-determined orbital
parameters and are included in the EOD.

ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
planet properties, such as mass-period, mass-radius?

@@

%KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata & \ref{sec:disc} \\
